On Secure Delegation of SampBQP with a Classical Client

### 2020-02-06 bqp.tex
Write rmk for FBQP
Add notes from Skype discussion

\begin{thm}
	There exists a constant-round and blind $\QPIP_0$ protocol with a classical client for $\BQP$ with negligible completeness and soundness.
\end{thm}

@@

Let $L\in\BQP$, and $x\in\set{0,1}^*$.

There exists some certificate for both $x\in L$ and $x\notin L\Rightarrow x\in\overline{L}$, since $L, \overline{L}\in\QMA$.
In fact, they have the same certificate $\ket{\psi_x}$ with some inverse polynomial gap between the completeness and soundness parameters.
See the excellent text \cite{kitaev2002classical} for details.
According to \cite{PhysRevA.93.022326}, the certificate can be check using only $X$ and $Z$ measurements.
We'll also summarize said proofs in \cref{sec:Hamiltonian} for our construction for $\SampBQP$.

\begin{thm}
	\protoref{BQP} is a $\QPIP_1$ and constant round protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}

@@

\begin{protocol}{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	Let $\lambda$ be the security parameter.
	Let $L$ be the depth of the circuit corresponding to $\cF$.
	Let $n$ be number of repetitions required to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	\begin{enumerate}
		\item The verifier runs $\mathsf{QHE.Keygen}(\lambda, L)$ to get $pk, sk$.
		\item The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\item The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ and $pk$ to the prover
		\item The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\item The verifier measures the incoming ciphertext according to \cref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates \Ethan{Not sure if rigorous enough}
		\item The verifier decodes the measurement results
		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{enumerate}
\end{protocol}

@@

\begin{thm}
	\protoref{BlindBQP} has negligible completeness in both $T$ and $\lambda$
\end{thm}
\begin{proof}
	Based on the correctness of $\mathsf{QHE}$, the verifier would successfully decode $\cF(c)$ with overwhelming probability.
	The subsequent underlying QMA check also has overwhelming probability of acceptance.
\end{proof}

@@

Now we can simply apply the following results from \cite{parallelrep} to obtain a blind and constant-round for $\QPIP_0$ with negligible completeness and soundness.
\begin{thm}
	There is a compiler that takes a $\QPIP_1$ protocol with the following properties:
	\begin{itemize}
		\item client's inputs are classical
		\item client doesn't applies any quantum gates, and uses only $X$ and $Z$ measurements
		\item completeness and soundness parameters are both negligible
	\end{itemize}
	and outputs a corresponding $\QPIP_0$ protocol with negligible completeness and soundness.
\end{thm}

\begin{rmk}
	The same construction works for $\FBQP$ too.
	\Ethan{Need to say more about amplification and doing this bit-by-bit. Also, where should I define $\FBQP$?}
\end{rmk}

>>>>

\begin{thm}
	There exists a constant-round and blind $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}

@@

Let $L\in\BQP$, and $x\in\set{0,1}^n$.

\Ethan{TODO cite MF instead}
There exists some certificate for both $x\in L$ and $x\notin L\Rightarrow x\in\overline{L}$, since $L, \overline{L}\in\QMA$.
In fact, they have the same certificate $\ket{\psi_x}$ with some inverse polynomial gap between the completeness and soundness parameters.
See the excellent text \cite{kitaev2002classical} for details.
According to \cite{PhysRevA.93.022326}, the certificate can be check using only $X$ and $Z$ measurements.
We'll also summarize said proofs in \cref{sec:Hamiltonian} for our construction for $\SampBQP$.

\Ethan{Consider citing Mahadev protocol 8.3 or theorem 8.4 instead}
\Ethan{Rewrite according to definition of $\BQP$ and yes/no instances}
\begin{thm}
	\protoref{BQP} is a $\QPIP_1$ protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}

@@

\begin{protocol}{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	Let $\lambda$ be the security parameter.
	Let $L$ be the depth of the circuit corresponding to $\cF$.
	Let $n$ be number of repetitions required to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	\begin{enumerate}
		\item The verifier runs $\mathsf{QHE.Keygen}(\lambda, L)$ to get $pk, sk$.
		\item The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\item The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ and $pk$ to the prover
		\item The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\item The verifier measures the incoming ciphertext according to \cref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates \Ethan{Not sure if rigorous enough}
		\item The verifier decodes the measurement results
		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
		\Ethan{No need; $\BQP$ is one-sided}
	\end{enumerate}
\end{protocol}

@@

\begin{thm}
	\protoref{BlindBQP} has negligible completeness in both $T$ and $\lambda$
	\Ethan{$\lambda$ and $T$ are poly. related, so keep $\lambda$ only.}
\end{thm}
\begin{proof}
	Based on the correctness of $\mathsf{QHE}$, the verifier would successfully decode $\cF(c)$ with overwhelming probability.
	The subsequent underlying QMA check also has overwhelming probability of acceptance.
\end{proof}

@@

Now we can simply apply the following results from \cite{parallelrep} to obtain a blind and constant-round for $\QPIP_0$ with negligible completeness and soundness.
\Ethan{Drop the theorem and explain in words. Mahadev's protocol compiles QPIP1 to QPIP0 but deteriorates soundness, and \cite{parallelrep} says parallel repetition works to recover good soundness guarantees.}
\begin{thm}
    \Ethan{TODO Not rigorous enough}
	There is a compiler that takes a $\QPIP_1$ protocol with the following properties:
	\begin{itemize}
		\item client's inputs are classical
		\item client doesn't applies any quantum gates, and uses only $X$ and $Z$ measurements
		\item completeness and soundness parameters are both negligible
	\end{itemize}
	and outputs a corresponding $\QPIP_0$ protocol with negligible completeness and soundness.
\end{thm}

\begin{rmk}
	Everything in this section easily generalizes to $\FBQP$. One simply repeats the process for every output bit.
	\Ethan{actually need 2 copies per bit now}
\end{rmk}
